SMT-Boosted Security Types for Low-Level MPC

### 2024-10-10 esop25/lang.tex
checkpoint

\section{$\minicat$ Syntax and Operational Semantics}

@@

\paragraph{Oblivious Transfer} A passive secure oblivious transfer (OT) protocol
based on previous work \cite{barthe2019probabilistic} can be defined
in $\minicat$, albeit assuming some shared randomness. Alternatively,
a simple passive secure OT can be defined with the addition of public
key cryptography as a primitive. But given the diversity of approaches
to OT, we instead assume that OT is abstract with respect to its
implementation, where calls to OT in $\mathbb{F}_2$ are of the form
$\OT{\elab{\be_1}{\cid}}{\be_2}{\be_3}$ -- given a \emph{choice bit}
$\be_1$ provided by a receiver $\cid$, the sender sends either $\be_2$
or $\be_3$.  Critically, the sender learns nothing about $\be_1$ and
the receiver learns nothing about the unselected value. We return to
the formal interpretation of OT in Section \ref{section-smt}.

>>>>

\section{$\minicat$ Syntax and Operational Semantics}
\label{section-lang}

@@

\paragraph{Oblivious Transfer} A passive secure oblivious transfer (OT) protocol
based on previous work \cite{barthe2019probabilistic} can be defined
in $\minicat$, albeit assuming some shared randomness. Alternatively,
a simple passive secure OT can be defined with the addition of public
key cryptography as a primitive. But given the diversity of approaches
to OT, we instead assume that OT is abstract with respect to its
implementation, where calls to OT in $\mathbb{F}_2$ are of the form
$\OT{\be_1}{\cid}{\be_2}{\be_3}$ -- given a \emph{choice bit}
$\be_1$ provided by a receiver $\cid$, the sender sends either $\be_2$
or $\be_3$.  Critically, the sender learns nothing about $\be_1$ and
the receiver learns nothing about the unselected value. We return to
the formal interpretation of OT in Section \ref{section-smt}.
